\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{{DIRECTOR / SECURITY OPERATIONS CENTER \hfill MAY 2020 --- Present}}
\subtext{Fannie Mae \hfill Reston, VA}
\begin{zitemize}
 \item Provides leadership and coordination in the planning, development, implementation and operation of company-wide, integrated security systems, to include detective and preventative controls, network and endpoint based security tools and configurations.
\item Responsible for maintaining and advancing all areas of the Security Operations Center (SOC); including Detection, Incident Response, Cyber Intelligence, Insider Threat and Cyber Incident Management; staff of 32.
\item Ensure the SOC can deliver on core objectives while the company transitions away from physical data centers and moves services into the cloud; including Amazon Web Services (AWS), Google Cloud Platform (GCP), and various Software as a Service (SaaS) providers.
\item Participates in Security and Privacy Emergency Response Leadership Team; provides input and subject matter expertise regarding internal and external organizational incidents/legal matters.
\item Recommends, participates in the development of, and establishes company security policies and procedures; establishes and implements short- and long-range departmental goals, objectives, policies, and operating procedures; monitors and evaluates program effectiveness; effects changes required for improvements.
\item Develops and manages annual budgets for the organization and performs periodic cost and productivity analyses; plans and develops strategies and programs for cost savings opportunities/increased capabilities.
\item Serves as a principal point of collaboration, leadership, and expertise to both internal and external constituencies on professional and operational matters pertaining to the mission, goals, objectives, and scope of the program.
\item Oversees all facets of the daily operations of the SOC, ensuring compliance with the Company, FHFA, state, and federal laws, policies, and regulations.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{MANAGER / INCIDENT RESPONSE \& THREAT HUNT \hfill OCT 2016 --- MAY 2020}}
\subtext{Fannie Mae \hfill Reston, VA}
\begin{zitemize}
\item Provides supervision of Incident Response and Threat Hunting personnel, which includes work allocation, training, promotion, enforcement of internal procedures and controls, and problem resolution; evaluates peak performance and makes recommendations for personnel actions; motivates employees to achieve peak productivity and performance; 8 direct reports.
\item Responsible for the execution and delivery of the incident response services for internal business
customers and coordination of response actions and plans as part of an integrated Cyber Team with Threat Intelligence, Detection, and Vulnerability Management partners.
\item Served as technical lead on large and highly complex incident response engagements.
\item Lead the malware analysis working group made up of key technical resources.
\item Partner with peer cyber teams to modify existing capabilities based on changes to the threat landscape using both technical and non-technical measures.
\item Acts as a technical lead for other team members; coaches, mentors, and trains junior employees. 
\end{zitemize}
\newpage
%====================
% EXPERIENCE C
%====================
\subsection{{SENIOR TEAM LEAD / INCIDENT RESPONSE \hfill MAR 2014 --- SEP 2016}}
\subtext{Fannie Mae \hfill Reston, VA}
\bigskip
\subsection{{SENIOR TEAM LEAD / SECURITY OPERATIONS CENTER \hfill AUG 2013 --- FEB 2014}}
\subtext{Rockwell Automation \hfill Milwaukee, WI}
\bigskip
\subsection{{SENIOR ANALYST / INCIDENT RESPONSE \hfill SEP 2012 --- JUL 2013}}
\subtext{Rockwell Automation \hfill Milwaukee, WI}

\begin{zitemize}
\item Integral part of the Computer Security Incident Response Team tasked with identifying, analyzing and remediating known vulnerabilities and exploits from Advanced Persistent Threats.
\item Coordinates the identification, containment, eradication, and recovery of high/critical incidents. 
\item Provides second level monitoring and investigation of information security events generated by complex network, endpoint, and log analysis platforms. 
\item Detects and analyzes malware using static and dynamic analysis techniques with tools such as IDA, Ollydbg, Capturebat, LordPE, ChimpREC, Process Monitor, and Process Hacker. 
\item Performs forensic analysis of suspected or known compromised systems and servers using EnCase Enterprise, Volatility and custom Live Response tools.
\item Managed workflow and updating of incident management and trouble ticket systems. 
\item Gives recommendations for better tuning and creation of signatures, rules, alerts, data parsers, and custom scripts. 
\item Monitors external information sources for situational awareness of the threat landscape. 
\item Utilized ticket tracking and wiki systems to document, log, and assist in the remediation of daily network security issues. 
\item Developed custom security tools to reduce incident response times and track tools, tactics and techniques of attackers. 
\item Acts as a technical lead for other team members; coaches, mentors, and trains junior employees. 

\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{DATA SECURITY ANALYST \ INCIDENT RESPONSE \hfill AUG 2010 --- SEP 2012}}
\subtext{Bucyrus International \ Caterpillar Global Mining \hfill South Milwaukee, WI}
\begin{zitemize}
\item Act as lead technical responder for Global Mining Computer Incident Response Team. Maintained 100\% reporting and incident closure SLA requirements. 
\item Planned, implemented and managed global vulnerability management solution utilizing Tenable Security Center. This program helped to identify internal and external risks to the company through our desktop, server and network infrastructures. This program has also been key in driving Global Mining to meet Caterpillar SRT patching requirements. 
\item Administrator of endpoint security products including Safend external device control, Wave Systems full disk encryption, Iron Mountain client backup. 
\item Responsible for conducting infrastructure security assessments and evaluating mitigating controls and usefulness to the business. 
\item Suggested and implemented project and process improvement ideas that resulted in time and money savings to the company. 
\item Facilitate the creation and maintenance of policies, standards and procedures promoting the overall security of the company by using experience and industry best practices.  
\item Give guidance for infrastructure projects to ensure security is maintained. This helped to strengthen the organizations overall security posture. 
\item Lead several internal investigations where digital evidence gathering and analysis was needed using EnCase Enterprise and open source solutions such as dd, The Skeuth Kit and Autopsy
\item Assisted with 3rd party penetration testing. 
\item Act as mentor to assist other team members, with this help other team members were more confident in their abilities and able to take on larger and more complex tasks and projects. 
\end{zitemize}

MORE EXPERIENCE AVAILABLE UPON REQUEST


\end{document}
